---
title: "Project Proposa"
author: "Group Members: Adriano Ponte, Lev Menzin, Sungkar Bolat, Derek Johnson"
date: "2023-04-05"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
nfl2022 = read.csv(".././data/play_by_play_2022.csv")

```



*Project Proposal*

The names of the students in the group.
A brief description of how the group will communicate and work together.
When during the week can the group meet? Consider needs of all group members.
What platforms will the group use to communicate and share documents.
The question or questions of interest that motivate the planned study.
The topic selected must be unanimous among group members.
Each question should be in the form of a research question which may be supported or refuted by the data analysis and typically proposes or predicts a relationship between some variables in the study.
Note that your project should aim to answer a limited number of questions (preferably one) using data from one or more source.
Do not try to answer too many questions. Better projects will have a focused set of one or two questions.
The source(s) of data.
A description of the data. Include in this description answers to these questions:
Who collected the data?
How were the data collected?
What are key variables in the data set, what do they measure, and how are they related to your key questions?
If the data may be thought of as a sample from some larger population, what is that larger population?
Note: if you get the data from a data repository such as Kaggle, you will need to dig into supplementary information to answer these questions.
It is insufficient to simply report a link to a Kaggle repository.
Include a description of a graph which will show how the data informs the primary question of interest.
Describe what variables you will include and what type of graph you will create.
Include a description of a possible model for the data and associated methods of inference or prediction.
We understand that you may not have a good grasp of these methods yet.
We understand the choice of methods may change between the proposal and the final project. **



*Meeting Schedule*
> Friday's at 8am in the first floor of the College Library.
> We communicate through discord and text groupchat.


*Possible Questions of Interest*
> Inference on a single population proportion. 
> We plan on focusing on the super bowl winner, The Chiefs, and how they stood out from the rest of the NFL. 
> Possible Questions of Interst include: 
    What variables have the biggest effect of Chief's success in winning the Super Bowl?
    How do the Chief's yards per play compare to the rest of the NFL?
    

*Description of Data*
> The data was scraped by nflfastR package.
> We plan to refine the data using this package among other R packages such as dplyr.
> According to nflfastr.com,  Nick Shoemaker captured the data in JSON format. Maksim Horowitz, Ronald Yurko, and Samuel Ventura crated the nflfastR package.

*Possible Project Model*
>First we have to find the means for our variables of interst.
> Then, compare averages of the Chiefs to those of the average NFL team.
> 
>
 
